Universal Anonymous Signatures

### 2022-08-13 prism-backend/research/gsac/app-related-proofs.tex
Updated proofs for UAS=>MPS.

  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
  Now, suppose that \adv~wins. Then, by assumption, the identity extracted by
  \adv~(which maps to a $\cid$ for \advB), does not belong to the set of corrupt
  users in \adv's game. By construction of \advB, then, $\OWNR[\cid] \notin \CU$
  in \advB's unforgeability game.
  \todo{The following seems wrong.}
  But it cannot belong to an honest user either,  
  as \adv's signature does not exist in \SIG. Otherwise, suppose it belongs to
  an honest user (in list \HU of \advB's game). Then, it breaks one-more
  unforgeability of the \SBCM scheme used by \CUASGen, as it is a valid.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
  \advB outputs whatever \adv~outputs, adding a $(\yinsp,iproof)$ pair, honestly
  generated from \adv's output. Note that the winning condition of \adv~
  requires that the produced signature belongs to an honest user, without
  having been produced via a call to the signing oracle. By construction of
  \advB, this directly makes \advB win in line 11 of the non-frameability game.
  %
  \qed
\end{proof}

>>>>

  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
  belong to the set of corrupt users in \adv's game. By construction of \advB
  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
  \CU$ in \advB's unforgeability game either.
  % 
  However, in order for \advB to win in its own game, we need to prove also that
  the produced identity does not belong to a user in \HU either. Suppose that it
  does. Simulation extractability ensures that the credentials extracted by
  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
  honest, its \usk has been produced uniformly at random, and has not been
  leaked to \adv~(as the issuer is also honest). Thus, the probability that
  the extracted credentials belong to an honest user is negligible and, if
  \adv~wins its game, \advB also does.
  %
  \qed
\end{proof}

@@

  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
  generated from \adv's output. Note that the winning condition of \adv~
  requires that the produced signature belongs to an honest user, without
  having been produced via a call to the signing oracle. By construction of
  \advB, this directly makes \advB win in line 11 of the non-frameability game.
  %
  \qed
\end{proof}

### 2022-08-13 prism-backend/research/gsac/app-uas-proofs.tex
Updated proofs for UAS=>MPS.

  \paragraph{(e) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accepts calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

@@

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]

@@

  First, suppose that the \Sig that \adv~outputs at line 2 exists in \SIG, for
  some \uid. In that case, the signature is accepted by \Verify at
  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

  Next, we prove that, after zero-knowledge and simulation extractability of
  $\NIZKRel_{\Sign}$, and blindness of \SBCM, $\Sig \in \SIG$ except with
  negligible probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by
  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
  compare $x$ and $w$ to the public and private key of a signature algorithm,
  respectively. In $\NIZKRel^{\Sign}$, $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\Eek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign outputs a valid
  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
  \Eek)$. Note that this witness must include some \usk which,
  for \adv~to win the game, must belong to an honest user. However, since the
  user (whichever it is) has not been corrupted, its \usk has not been leaked
  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
  that the issuer (who is potentially corrupt), did not learn \usk either during
  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
  \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}

>>>>

  \paragraph{(e) All {\cred}s are bound to the \usk of a known \uid.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain the same \usk as their user key
  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
  \uid exists (but not because more than one \cid belongs to different {\uid}s).
  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
  since they only accept calls from known {\uid}s (either in \HU or \CU,
  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
  least one such credential must have been used to produce the signature, then
  this breaks the one-more forgery property of the underlying \SBCM.
  %
  \qed
\end{proof}

@@

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
  \label{prf:frame-uas}

@@

  Since the signature output by \adv~is accepted by \Verify at line 4,
  simulation extractability of $\NIZK^{\Sign}$ ensures that $\yeval = \yeval^0$,
  and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
  pair output by \adv~is accepted by \Judge, simulation extractability of
  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$.

  Next, we prove that, after zero-knowledge and simulation extractability of
  $\NIZKRel_{\Sign}$, and blindness of \SBCM, no credential from an honest user
  can be extracted from the signature output by \adv, except with negligible
  probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by
  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
  compare $x$ and $w$ to the public and private key of a signature algorithm,
  respectively. In $\NIZKRel^{\Sign}$, $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\Eek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign outputs a valid
  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
  \Eek)$. Note that this witness must include some \usk which, in case of
  being owned by an honest user, has not been leaked to \adv~--as the user
  has not been corrupted, nor the \usk has been leaked via \SIGN queries,
  where the proof of knowledge within \Sign is now simulated). Moreover,
  blindness of \SBCM ensures that the issuer (who is potentially corrupt), did
  not learn \usk either during calls to \OBTAIN. Thus, since \usk is picked
  uniformly at random by honest users, the probability that $\UK[\uid] = \usk$
  for $\uid \in \HU$ and \Sig produced by the adversary, is negligible.
  %
  \qed
\end{proof}
